Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling

### 2021-01-28 papers/intro_paper/results_lvc.tex
started to go through LVC results section

\ab{Furthermore}, for the first time, in this paper, we \ab{apply our method to
measure the QNMs to} \sout{present results on} the relevant
GW events from LIGO-Virgo's O1 and O2 runs, alongside
the above events. Applying the same thresholds as above, we find three
additional events that could be included in the analysis: GW150914,
GW170104, GW170729. The other high-mass events from O1-O2, GW170809,
GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the
merger-ringdown signal. For the three relevant signals, GW150914,
GW170104 and GW170729, we \sout{provide} \ab{show} the posterior distributions in
$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also
reconstruct the \sout{effective} QNM parameters, $(\fngr{220}, \taungr{220})$
which are tabulated in Table~\ref{tab:qnm_o1o2_results} \footnote{See
  Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
  thresholds. The paper quotes them for the purpose of the IMR
  consistency test, but the same thresholds have been used for the
  $pSEOB$ test, as well.} Among all the GW signals detected so far,
GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its
loudness, \sout{mass as well as the clarity of the signal,} \comment{AB: what
is the ``clarity'' of a signal?} leading to the
first, and to date, best attempt in measuring the QNM frequencies~\cite{}.

>>>>

Furthermore, for the first time, in this paper, we apply our method to
measure the QNMs to the relevant
GW events from LIGO-Virgo's O1 and O2 runs, alongside
the above events. Applying the same thresholds as above, we find three
additional events that could be included in the analysis: GW150914,
GW170104, GW170729. The other high-mass events from O1-O2, GW170809,
GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the
merger-ringdown signal. For the three relevant signals, GW150914,
GW170104 and GW170729, we show the posterior distributions in
$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also reconstruct the QNM parameters, $(\fngr{220}, \taungr{220})$
which are tabulated in Table~\ref{tab:qnm_o1o2_results} \footnote{See
  Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
  thresholds. The paper quotes them for the purpose of the IMR
  consistency test, but the same thresholds have been used for the
  $\pSEOB$ test, as well.} Among all the GW signals detected so far,
GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its
loudness, leading to the first, and to date, best attempt in measuring the QNM frequencies~\cite{LSC_2016grtests,Brito:2018rfr,Carullo:2019flw,Isi:2019aib}.
